During my P.h.D studies, I made a contribution to the 1000 person LHCb particle physics experiment, thus the work of this thesis is a combination of the author's own contribution and the contribution of others. I have been involved in two main projects.

The first one was related to the improvement of the Downstream Tracking algorithm described in Chapter \ref{chapter:PLLT}. The goal of this project was to enhance one of the track reconstruction algorithms dedicated to finding so-called, long-lived neutral particles via the application of Machine Learning. This project has allowed me to get practical knowledge on building a full Machine Learning pipeline and track reconstruction algorithm. I was responsible for preparing, cleaning, and visualization of the training data, selecting the classification model, monitoring and visualization training progress, validating, and interpretation of the model’s prediction. The algorithm has passed a very demanding testing procedure and has subsequently been commissioned and added to the real-time event trigger system of the LHCb experiment.
Secondly, I was a member of the LHCb UT testbeam team. Within this project, I made a significant contribution to modernizing the LHCb detector by implementing the whole monitoring processing chain for the Upstream Tracker (UT). This software, called TbUT, is described in Chapter~\ref{chapter:tbut}. It was used to analyze the data collected during the number of testbeam campaigns as well as it will be a key component of the future monitoring and calibration tool for the UT detector. Besides implementing the aforementioned software, I took part in data-taking shifts at CERN. I made a contribution to this data analysis, which is a topic of Chapter \ref{chapter:testbeam}.

In addition to the research duties, I have an excellent teaching opportunity at both undergraduate and graduate levels. I was responsible for AGH course Python in the Enterprise. During this course, the students have the opportunity to get familiar with such concepts as Unit Testing, Design Patterns, Continuous Integration, and Machine Learning. The key part of my teaching duties was supervising group projects. The projects that a group of students was focused mostly on image processing using Deep Learning (car plates recognition, sudoku solver using camera image captured, emotion detection).

The list of papers with my contribution, conferences, and summer schools that I participated in is provided below. 

\newpage

\section*{Publications}
			\begin{itemize}
			    \item \textbf{Machine learning based lonTg-lived particle reconstruction algorithm for the LHCb experiment},\\ NeuralPS workshop "Machine Learning and the Physical Sciences"  (\textcolor{red}{\href{https://ml4physicalsciences.github.io/2020/files/NeurIPS_ML4PS_2020_148.pdf}{paper}},\textcolor{red}{\href{https://ml4physicalsciences.github.io/2020/files/NeurIPS_ML4PS_2020_148_poster.pdf}{poster}});
			    \item \textbf{PatLongLivedTracking: a tracking algorithm for the reconstruction of the daughters of long-lived particles in LHCb};\\ LHCb-PUB-2017-001;
				\item \textbf{Emulation and Calibration of the SALT Read-out Chip for the Upstream Tracker for Modernised LHCb Detector}; \\
				Acta Phys. Pol. B 46 (2015) 1263-1269;
				\item \textbf{Testbeam studies of pre-prototype silicon strip sensors for the LHCb UT upgrade project};  \\
				Nucl.Instrum.Meth. A806 (2016) 244-257;
				\item \textbf{Signal coupling to embedded pitch adapters in silicon sensors};\\
				Nucl.Instrum.Meth. A877 (2018) 252-258.
			\end{itemize}

%---------------------------------------------------------
\section*{Conferences}
\begin{itemize}
                \item \textbf{ML in PL Conference 2019 } Machine learning in High Energy Physics (\textcolor{red}{\href{https://www.youtube.com/watch?v=6cO2OBhJlDQ\&list=PLoaWrlj9TDhPf08oDhBspvSP11E_uXSnB&index=39}{recording}});
                \item \textbf{76th LHCb Analysis and Software week} Building and validating MVAs, How to build more reliable ML models (\textcolor{red}{\href{https://docs.google.com/presentation/d/14ZELcsYN_eMCpxtsYzOmIaC_o8rhU6abqH1jwxCijZI/edit?usp=sharing}{slides}});
                
			    \item \textbf{8th International Conference on New Frontiers in Physics (ICNFP 2019)}; Machine Learning techniques used in LHCb analyses and online applications;
			    \item  \textbf{LHCP, Bologna, 4-9 June 2018} A tracking algorithm for the reconstruction of the daughters of long-lived particles in LHCb;
				\item \textbf{Connecting the Dots/Inteligent Tracker; 2017;} Deep Neural Nets and Bonsai BDTs in the LHCb pattern recognition;
				\item \textbf{XXII Cracow Epiphany Conference on Physics in LHC Run II; 2016;} Calibration and monitoring of the SALT readout ASIC for the LHCb UT detector;
				\item \textbf{XXI Cracow Epiphany Conference on future of High Energy Collider; 2015;} Emulation and calibration of the SALT readout chip for the UT tracker for modernised LHCb detector.
			\end{itemize}
			
\section*{Summer schools}
\begin{itemize}
    \item \textbf{Wolfram Summer School}, July 2017, Waltham MA, USA, 
    \begin{itemize}
        \item Worked on project DeepLaetitia: Deep Reinforcement Learning That Makes You Smile (\textcolor{red}{\href{https://education.wolfram.com/summer/school/alumni/2017/dendek/}{project summary}});
    \end{itemize}
    \item \textbf{Second Machine Learning in High Energy Physic Summer School 2016}, July 2016, Lund Sweden 
    \item \textbf{The 3rd Asia-Europe-Pacific School of High Energy Physics}, October 2016, Beijing China
    \item \textbf{The 38th CERN School of Computing}, September 2015, Kavala Greece
\end{itemize}